---
title: "lab5-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab5-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab5)
```

## Setup
To install the lab5 package, source it from GitHub with the command `devtools::install_github("Marbr987/lab5")`.

## Usage of the package

The `get_coordinates` function takes a city name as a string as input and outputs a named vector with the longitude and the altitude coordinate of the city. If the city is not located in Sweden, a message is printed (see examples below).
```{r}
get_coordinates("Stockholm")
get_coordinates("Berlin")
```

Furthermore, the package provides a Shiny app. In the app, two cities can be entered, which are displayed on a map of Sweden and their coordinates printed. The two input cities must be located in Sweden, otherwise an error message is displayed.
The app provides a slider to define a p-value, for which the p-norm distance between the two cities is calculated. A plot illustrates the p-norm distances between the cities for different p-values.
The Shiny app can be opened with `runGitHub()`.
